Preprocessing overview

### 2021-02-18 inst/examples/language.Rmd
ok

 * `r length(unique(unlist(strsplit(as.character(df$languages), ";"))))-1` [unique languages](output.tables/language_accepted.csv)
 * `r length(unique(df$language_primary))-1` [unique primary languages](output.tables/language_accepted.csv)  
 * `r sum(!df$multilingual, na.rm = TRUE)` single-language documents (`r round(100 * mean(!df$multilingual, na.omit = TRUE), 2)`%)
 * `r sum(df$multilingual, na.rm = TRUE)` multilingual documents (`r round(100 * mean(df$multilingual, na.omit = TRUE), 2)`%) 
 * [Conversions from raw to preprocessed language entries](output.tables/language_conversions.csv) 
 * `r sum(is.na(df$languages) | df$language_primary == "Undetermined")` documents (`r round(100*mean(is.na(df$languages) | df$language_primary == "Undetermined"), 2)`%) with [unrecognized language](output.tables/language_discarded.csv)

@@

@@

```{r summarylang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=5}
top_plot(df, "languages", ntop = ntop, log10 = TRUE) 
```

Number of documents assigned with each language (top-10). For a complete list,
see [accepted languages](output.tables/language_accepted.csv).

>>>>

 * `r length(unique(unlist(strsplit(as.character(df$languages), ";"))))-1` [unique languages](output.tables/languages_accepted.csv)
 * `r length(unique(df$language_primary))-1` [unique primary languages](output.tables/language_primary_accepted.csv)  
 * `r sum(!df$multilingual, na.rm = TRUE)` single-language documents (`r round(100 * mean(!df$multilingual, na.omit = TRUE), 2)`%)
 * `r sum(df$multilingual, na.rm = TRUE)` multilingual documents (`r round(100 * mean(df$multilingual, na.omit = TRUE), 2)`%) 
 * [Conversions from raw to preprocessed language entries](output.tables/language_conversions.csv) 
 * `r sum(is.na(df$languages) | df$language_primary == "Undetermined")` documents (`r round(100*mean(is.na(df$languages) | df$language_primary == "Undetermined"), 2)`%) with [unrecognized language](output.tables/language_discarded.csv)

@@

Number of titles assigned with each language (top-10). For a complete list,
see [accepted languages](output.tables/language_accepted.csv).

@@

```{r summarylang, echo=FALSE, message=FALSE, warning=FALSE, fig.width=7, fig.height=5}
top_plot(df, "languages", ntop = ntop, log10 = TRUE) + labs(y = "Entries (n)")
```

### 2021-02-18 inst/examples/overview.Rmd
ok

  * [Author info](author.md)
  * [Gender info](gender.md)
  * [Publisher info](publisher.md)
  * [Publication geography](publicationplace.md)
  * [Publication year info](publicationyear.md)
  * [Titles](title.md)  
  * [Page counts](pagecount.md)
  * [Physical dimension](dimension.md)    
  * [Document and subject topics](topic.md)
  * [Languages](language.md)

See also [further preprocessing details](details.Rmd).

>>>>

  * [Author info](author.md)
  * [Gender info](gender.md)
  * [Publisher info](publisher.md)
  * [Publication geography](publication_place.md)
  * [Publication year info](publication_time.md)
  * [Publication year info](publication_frequency.md)
  * [Publication year info](publication_interval.md)  
  * [Titles](title.md)  
  * [Page counts](pagecount.md)
  * [Physical dimension](dimension.md)    
  * [Document and subject topics](topic.md)
  * [Languages](language.md)
  * [Corporate](corporate.md)
  * [Holder](holder.md)
  * [Note_510c](note_510c.md)
  * [Note_dissertation](note_dissertation.md)
  * [Note_granter](note_granter.md)
  * [Note_source](note_source.md)
  * [Subject_topic](subject_topic.md)
  * [Successor](successor.md)
  * [Title_uniform](title_uniform.md)
  * [Uncontrolled](uncontrolled.md)
See also [further preprocessing details](details.Rmd).
